Boolean Operations for Surfaces in VTK Without External Libraries

### 2011-05-10 Document/LaTeX/Article.tex
Add docs on methods in vtkPolyDataDistance.

@@

To support boolean operations, we introduce another class, \code{vtkPolyDataDistance}, that computes the distance from the first input \code{vtkPolyData} to a second. Optionally, the distance field from the second input \code{vtkPolyData} to the first can also be computed. These distances are computed at points in the mesh and are stored as a point data field named ``Distance''.

>>>>

\subsection{vtkImplicitPolyData}

@@

\subsection{vtkPolyDataDistance}

To support distance-based boolean operations, we introduce another class, \code{vtkPolyDataDistance}, that computes the distance from points in the first input \code{vtkPolyData} to a second by evaluating the signed distance field from the second input using the \code{vtkImplicitPolyData} class. Optionally, the distance from points in the second input \code{vtkPolyData} to the first can also be computed. These distances are stored as a point data field named ``Distance''.

\code{vtkPolyDataDistance} has some options. Use the methods
\begin{verbatim}
void SetSignedDistance(int value);
void SignedDistanceOn();
void SignedDistanceOff();
\end{verbatim}
to turn computation of the signed distance on or off. By default, this option is on. If it is off, the unsigned distance function is computed.

The methods
\begin{verbatim}
void SetNegateDistance(int value);
void NegateDistanceOn();
void NegateDistanceOff();
\end{verbatim}
can be used to enable or disable negation of the signed distance field. If the \code{SignedDistance} option is off, then this option has no effect. \code{NegateDistance} option is off by default.

The methods
\begin{verbatim}
void SetComputeSecondDistance(int value);
void ComputeSecondDistanceOn();
void ComputeSecondDistanceOff();
\end{verbatim}
enables computation of the signed distance for the second input. Finally, a convenience method
\begin{verbatim}
vtkPolyData* GetSecondDistanceOutput();
\end{verbatim}
can be called to get the second output.
